\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with continuum detection in the foreground lensing FR-II radio galaxy at $z$ = 0.685

### 2015-06-25 skeleton.tex
Recent changes, re remove 3C core stuff

The resulting best-fit model as shown in Figure \ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
The best-fit model yields a magnification
factor of $\mu_{\rm 1mm}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
$M_{\odot}$ and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ $M_{\odot}$, respectively. All best-fit
parameters are listed in Table \ref{tab:lensParam}.
\input{table_lensParams}

@@

We detect the radio continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 mJy at $\nu_{\rm cont}$ = 104.2106 GHz 
(2.877 mm) in the observed-frame. In this lens system, the foreground galaxy (3C220.3) is a double-lobed FR-II radio galaxy, 
hence we expect the continuum to be dominated by emissions from the foreground galaxy. At this frequency, previous studies have suggested that contributions from the radio core dominates over that from the radio lobes and jets (cite).

Talk about the radio core:
\citet{Mullin06a} report an upper limit on the radio core of blah mJy at 4.6 GHz, whereas \citet{Haas14} 
report a detection of the radio core of 0.8 mJy at 9 GHz. 
We fit a functional form for the radio lobe to NED data following Equation (1) by \citet{Cleary07a} and references therein:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.
$\nu_t >$ 1 MHz, 30 GHz $< \nu_c^{\rm lobe}$ 3000 GHz.
, extrapolate to continuum 
frequency = blah mJy. which is consistent with our continuum measurement.

We estimated the radio core contribution at our continuum frequency by taking two FR-II galaxies from the
3C catalog that have measurements on the radio core. Shows at these frequencies, what the radio core contribution is like
 thus we 
expect the emission from the core component to dominate our continuum measurement; however, the integrated flux density is measured 
to be 7.18 $\pm$ 0.69 mJy. Since the orientation of the synthesized beam aligns with the axis along the 
lobes of the radio galaxy as shown in Figure \ref{fig:cont}, we interpret the difference in the peak flux 
density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the continuum detection 
includes emissions from the lobes. Furthermore, the contours of the 104 GHz continuum are
centered on the north lobe of the radio galaxy in the overlay image, this further supports our argument.

Therefore the 10$\sigma$ detection of the partially resolved continuum emission suggests a 
non-negligible contribution coming from the lobe emission, the peak flux density therefore does not corresponds to the core 
emission.

\input{table_SED}
The continuum data used in plotting the SED of 3C220.3 is listed in Table \ref{tab:SEDdataRadio}

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3FullSED}
\caption{Figure shows the SED of 3C220.3 and SMM J0939 including the new measurements presented in this paper. 
Black markers represent existing data of 3C220.3 (see table \ref{tab:SEDdataRadio}). Red markers at 104 GHz corresponds to 
our continuum measurements (integrated, peak, and difference). The dashed black line corresponds to the parabolic function we 
fit to the data associated with the radio galaxy following \citet{Cleary07a} and references therein. The dashed blue line and 
the dashed dot magenta line correspond to the best-fit SED of the background galaxy using an optically thick model, and an 
optically thin model, respectively. \label{fig:SED}}
\end{figure}

\subsubsection{SMM J0939+8315} 
\input{table_SEDphoto}
%burn-in phase 100, walkers 500, steps 500,
To constrain the dust and gas properties in the ISM of SMM J0939, we perform SED fitting based on the
photometric data obtained using the Spitzer Space Telescope and the {\it Herschel} Space Telescope, at wavelengths
between observed-frame 70 \micron-1000 \micron, and the SMA interferometric data at 1 mm (Table \ref{tab:SEDdataSMG}. We use the publicly
available software {\sc mbb\_emcee} to perform SED fitting, the code uses an affine-invariant Markov chain Monte
Carlo (MCMC) approach, the details are described by \citet{Riechers13a} and \citet{Dowell14a}. The
functional form of the fit comprises of a modified blackbody function with a power law S$_{\lambda} \propto \lambda^\alpha
$ attached to the blue
side.
We fit both an optically thick and optically thin model. In the optically thick case, the wavelength $
\lambda_0$ = $\frac{c}{\nu_0}$ is an additional parameter which represents where the optical
depth $\tau_{\nu}$ = ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
in the optically thick regime is as follows:
\begin{equation}
\rm S_{\lambda} \propto \frac{(1-exp^{-(\frac{\lambda_0 (1+z)}{\lambda})^{\beta}})(\frac{c}{\lambda})^3}
{exp^{\frac{hc}{\lambda\rm{kT/(1+z)} } }-1}
\end{equation}
and in the optically thin regime, the functional form reduces to:
\begin{equation}
\rm S_{\lambda} \propto \frac{(\frac{c}{\lambda})^{\beta+3}}{exp^{\frac{hc}{\lambda\rm{kT/(1+z)}}}-1}
\end{equation}
where T is the rest-frame characteristic cold dust temperature (fitting to the FIR part), $\lambda_0$ is rest-frame wavelength
where the optical depth reaches unity, $\beta$ is the dust emissivity (or spectral index of the dust extinction
curve), and $\alpha$ is the power law spectral index. The overall fit is normalized using the observed-frame 500
$\micron$ flux density, hence this becomes an additional parameter in the fit. In both models, we impose an upper limit on $
\lambda_0$ to 2000 \micron, and the observed-frame dust temperature $T_{\rm d}/(1+z)$ to 60 K. We fix the upper limit on 
$\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.

\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}. The best-fit solution of an optically thin
model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than the optically thin
model. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.33$^{+1.14}_{-1.13}\times$10$^{12}L_
\odot$, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.52$^{+2.62}_{-2.63}\times$10$
^{12}L_{\odot}$. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg$^{-1}$ at 125.0 $
\micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
\begin{equation}
\mathrm{M_{\rm dust}} = S_{\nu} \times D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \times \tau_{\nu} [1-
\exp(-\tau_{\nu})]^{-1}
\end{equation}
where $S_{\nu}$ is the flux density, $D_{\rm L}$ is the luminosity distance, $\kappa_{\nu}$ is the dust
absorption coefficient, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$ =
50.47$^{20.42}_{-20.15}\times$10$^8 M_{\odot}$. These values are based on SED fitting to the photometric data, i.e. prior
to lensing correction.

NOTE:
using beta upper limit 3.0, getting very different beta, and dust mass dot dot dot

\begin{figure}[!tbp]
\centering
\includegraphics[width=0.5\textwidth]{Figure/CorrelationPlot__thick_testbeta}
\includegraphics[width=0.5\textwidth]{Figure/CorrelationPlot__thin_testSMA}
\caption{Resulting correlation plot from our SED fitting. Plots on the diagonal axes are marginalized posterior probability 
distribution of each
parameter. Off-diagonal plots are 2D histograms between parameters. Cross denotes where the best-fit value corresponds to in 
the 2D correlation plot. Top: Optically thick
model. Bottom: Optically thin model. The parameter T (consider making this to T/(1+z)) is the observed-frame characteristic dust temperature.
\label{fig:sedlikelihood}}
\end{figure}
%Our uncertainties on M$_{d}$ do not include the uncertainty in $K_{\nu}$, which is at least a factor of blah dex.
%In most cases, $\alpha$ is poorly constrained, with the fits only providing a lower limit. Because of the way the
%blue-side power law is joined to the MBB,
%this simply amounts to a statement that the merge point between the power law and the thermal SED lies at
%wavelengths lower than the shortest
%wavelength photometry point (250 micron). (in Dowell et al. 2014)

\subsection{Radio-FIR correlation}%%%%% ok, except add comparison.
% q correlation using IR: 2.81
We extrapolate the flux density at rest-frame 100 GHz based on the optically thick model; assuming a power law
spectral index of -0.8 in the radio domain of the SED, we calculate the corresponding rest-frame luminosity $L_{\rm 1.4}$. 
Together with the
integrated FIR luminosity with lensing correction, we derive the radio-FIR correlation parameter (q) using:
\begin{equation}
q = \log{10} \frac{L_{\rm FIR}} {9.8\times10^{-15}} L_{\odot} - \log{10}\frac{L_{\rm 1.4}} {\rm W\ Hz^{-1}}
\end{equation}
This yields $q$ = 2.59 $\pm$ blah. 
Compare to other galaxies blah. to be expanded BLAH
%$S_{\rm 1.4 GHz}$ = 0.45655848 mJy / mu (observed frame) mJy
q = 2.4 for FIR-selected galaxy (Ivison 2010a,b,c)

\subsection{Molecular gas mass}
%Equation: M$_gas$ = alpha$\times$L$_{\rm CO}$
Talk about the brightness temperature ratio $<$ 1 for SMG, and $\sim$ 1 for quasar, so we adopt 1 here since the source is 
hosting a quasar.

Frayer: Observations of CO(1-0) are key for deriving the total molecular gas mass. The CO(1-0) line traces the cold material 
not probed by the higher-level CO transitions. Unfortunately, most high-redshift sources to date have been observed in only the 
higher level J > 1 transitions, and many papers have assumed a single-component ISM that is fully thermalized with Tb 
(J>1) / Tb (1-0) = 1. However, recent CO(1-0) observations of the SMG population show that this assumption is not correct 
\citep[e.g.,][]{Harris10a,Carilli10a,Swinbank2010a,Ivison11a,Ivison10d}. From the compilation of 
these previous results, an average CO line ratio value of R31 = 0.6 pm 0.1 is found for a sample of nine SMGs.

Since only CO($J$ = 3 $\rightarrow$ 2) line has been detected on this object, we derive the molecular gas mass in
this SMG assuming thermalized excitation or assuming thermalized optically thick CO, i.e. the brightness temperature ratio 
between CO($J$ = 3 $\rightarrow$ 2)
and ($J$ = 1 $\rightarrow$ 0) is $R_{31}$ = 1 \citep[e.g.,][and references therein]{Riechers11a,Scott11a}
%(e.g., Ivison et al. 2008, 2012). 
We calculate the CO($J$ = 1 $\rightarrow$ 0) line luminosity using standard relations 
\citep[e.g.,][]{Solomon05a,Carilli13a}:
\begin{equation}
L^{\prime}_{\rm CO} = \frac{3.25\times10^7}{\nu_{\rm CO (3-2), rest}^2}\times \frac{D_L^2}{\mu} \times
\frac{I_{\rm CO(3-2)}} {R_{\rm 31} (1 + z)}
\end{equation}
this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ ($\mu$/9.74)$^{-1}$ [\rm K km s
$^{-1}$ pc$^2$]
after lensing correction. The inferred total molecular gas mass is therefore M$_{\rm gas}$ = 3.303$\times
$10$^{10}$ ($\alpha$/0.8) ($\mu$/9.74)$^{-1} M_\odot$. We assume a conversion factor of $\alpha_{\rm CO}$ =
0.8 M$_\odot$ (K Km s$^{-1}$ pc$^2$)$^{-1}$ based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep{Bothwell13a,Tacconi10a,Daddi2010a}. As derived in the previous section, SMM has a dust mass of M
$_{\rm dust}
$=50.47$^{20.42}_{-20.15}\times$10$^8\rm M_{\odot}$ (before lensing correction), this corresponds to a gas-to-dust
ratio of f$_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , which is in good agreement with the range 
of values found in other SMGs (cite).

@@

Follow-up CO(1?0) observations of three representative z ? 1.5 galaxies in the CO(1?0) line emission suggest that the molecular 
gas in these systems is already sub-thermally excited at the CO(3?2) transition similar to what is found in local disks 
(Dannerbauer et al. 2009; Aravena et al. 2010), with typical line brightness temperature ratios between both lines of ? 0.5. 
This is also similar to what is found in SMGs (Harris et al. 2010; Ivison et al. 2011; Bothwell et al. 2013), but substantially 
different to high-redshift QSOs, which appear to have highly excited gas with line temperature ratios close to unity (Riechers 
et al. 2006; Weiß et al. 2007; Ao et al. 2008; Riechers et al. 2011a; Ivison et al. 2012, e.g.,). Recent observations of z ? 
0.3 disk galaxies support these findings, indicating that the molecular gas content, as traced by CO(1?0), is two times larger 
than expected from J > 3 CO measurements, comparable to z > 2 SMGs (Papadopoulos \& Ivison 2002; Harris et al. 2010; 
Ivison et al. 2011; Riechers et al. 2011c). 
% Michalowski et al. 2010, Santini et al. 2010
% typical of local ULIRs is ~ 100)
%\citep{Riechers2011a}

\subsection{Star formation rate}
We derive the star formation rate (SFR) using the modified \citet{Kennicutt98a} relation, assuming a \citet{Chabrier03a}
stellar initial mass (IMF) function: SFR = 1.0 $\times$ 10$^{-10}\times$ ($L_{\rm IR\ or\ FIR}$). This yields SFR$_{\rm IR}$ 
= (909.12$\pm$155.67) $\times\ (\mu/9.74)^{-1}$ [$M\sun$ yr$^{-1}$] and SFR$_{\rm FIR}$ 547.71$\times(\mu/9.74)^{-1}$ [M$
\sun$ yr$^{-1}$] using lensing-corrected (far-)infrared luminosities (L$_{\rm IR}$ and L$_{\rm FIR}$) derived from our SED 
fitting, and assuming negligible contribution from AGN.

Assuming constant SFR, the minimum time for which the starburst in SMM J0939 can be maintained at its
current SFR is approximated by the gas depletion timescale $\tau$ = M$_{\rm gas}$/SFR, which is $\tau_{\rm IR}$ = 36.33 
Myr, and $\tau_{\rm FIR}$ = 60.30 Myr.
Compare THIS NUMBER: with other SMGs (e.g., \citep{Greve05a}).

\subsection{SFE}
%SFE using LIR: 220.22
%SFE using LFIR: 132.68
% The ratio between LIR ($\propto$ SFR) and L$^\prime$CO ($\propto$ Mgas)
Frayer: Since the IR luminosity is proportional to the SFR and the CO L is proportional to the molecular gas mass, the IR-to-
CO L ratio provides an indication of the SFE. Strong starburst and ULIRGs tend to show high IR-to-CO L ratios of $gtsim$ 
100 L$\sun$ ( K km/s pc2)-1 \citep[e.g.,][]{Solomon05a}. 
\citet{Greve05a} found an average L(IR)/L$\prime
$CO ratio for SMGs which was a factor of two larger than that for local ULIRGs

The SFR per unit mass of molecular gas is commonly taken as a
measure of the star formation efficiency, SFE = SFR/M$_{\rm gas}$. We compute the ratio using lensing-corrected (far-)infrared 
luminosities (L$_{\rm IR}$ and L$_{\rm FIR}$) and CO($J$ = 1 $\rightarrow$ 0) luminosity SFE = L$_{\rm F/IR}$/L$^
\prime_{\rm CO(1-0)}$, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ and is independent of the 
choice of IMF,
assuming no differential lensing between the CO and infrared emission.

@@

We find a ratio of SFE$_{\rm IR}$ = 220.22 and SFE$_{\rm FIR}$ = 132.68, which are comparable
to what is found in "typical" SMGs (tacconi et al. 2006, Riechers et al. 2010, cite).
Note: SFE values for ULIRGs and distant SMGs typically exceed 100 L$_\odot$ [K km/s pc$^2$]$^{-1}$
(e.g., Yao et al. 2003; Neri et al. 2003; Greve et al. 2005; Bouche et al. 2007).

\subsection{Dynamical mass} %% check half light radius error, and comparison
We derive the dynamical mass of SMM J0939 using an isotropic virial estimator (e.g., Engel et al. 2010):
\begin{equation}
M_{\rm dyn} = 2.8\times 10^5 \times \Delta \rm v_{\rm line}^ 2 \times r\ [kpc]
\end{equation}
where the line width $\Delta \rm v_{\rm line}^ 2$ is based on our CO($J$ = 3 $\rightarrow$ 2) line
measurement and the half-light radius is based on our lens model, $r$=0\farcs023484 $\pm$ 0\farcs033. This yields gas-to-
dynamical mass fraction of f$_{\rm gas-to-dyn}$ = 2.03.

Compare to other. blah blah blah dynamical mass?, is it consistent with molecular gas mass?

\subsection{Surface mass density}

\section{Discussion And Conclusions} \label{sec:conclusions}
We present blah...

@@

look at "Lensed QSOs at high z observational, CO measurements (DB)" note

%\acknowledgments
%Facilities: \facility{CARMA}

@@

\input{table_SMG}

>>>>

The resulting best-fit model as shown in Figure \ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
The best-fit model yields a magnification
factor of $\mu_{\rm 1mm}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
\Msun and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ \Msun, respectively. All best-fit
parameters are listed in Table \ref{tab:lensParam}.
\input{table_lensParams}

@@

We detect the radio continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 mJy at $\nu_{\rm cont}$ = 104.2106 GHz 
(2.877 mm) in the observed-frame. In this lens system, the foreground galaxy (3C220.3) is a double-lobed FR-II radio galaxy, 
hence we expect the continuum to be dominated by emissions from the foreground galaxy.

====== I will edit this: \\
Previous studies suggest that at 104 GHz, contributions from the radio core dominates over that from the radio lobes and jets (cite), thus we 
expect the emission from the core component to dominate our continuum measurement; however, the integrated flux density is measured 
to be 7.18 $\pm$ 0.69 mJy. Since the orientation of the synthesized beam aligns with the axis along the 
lobes of the radio galaxy as shown in Figure \ref{fig:cont}, we interpret the difference in the peak flux 
density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the continuum detection 
includes emissions from the lobes. Furthermore, the contours of the 104 GHz continuum are
centered on the north lobe of the radio galaxy in the overlay image, this further supports our argument. 
\citet{Mullin06a} report an upper limit on the radio core of 0.17 mJy at 4.6 GHz, whereas \citet{Haas14} 
report a detection of the radio core of 0.8 mJy at 9 GHz, as shown in Figure \ref{fig:SED}.\\
====== Please keep on reading from here.

We fit the SED of the radio galaxy using previous data listed in Table \ref{tab:SEDdataRadio}, following Equation (1) by \citet{Cleary07a}, the fit can be expressed as a functional form:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution. 
\\ ====== I will edit this ====
In their paper, they limit $\nu_t >$ 1 MHz, 30 GHz $< \nu_c^{\rm lobe}$ 3000 GHz, which give best-fit parameters, and we use their parameters to plot the fit, and we extrapolate to 104 GHz, which is = blah mJy, which is consistent with our continuum measurement. Therefore the 10$\sigma$ detection of the partially resolved continuum emission suggests a 
non-negligible contribution coming from the lobe emission, the peak flux density therefore does not corresponds to the core 
emission. 
\\ ==================
\input{table_SED}

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3FullSED}
\caption{Figure shows the SED of 3C220.3 and SMM J0939 including the new measurements presented in this paper. 
Black markers represent existing data of 3C220.3 (see table \ref{tab:SEDdataRadio}). Red markers at 104 GHz corresponds to 
our continuum measurements (integrated, peak, and difference). The dashed black line corresponds to the parabolic function we 
fit to the data associated with the radio galaxy following \citet{Cleary07a}. The dashed blue line and 
the dashed dot magenta line correspond to the best-fit SED of the background SMG, using an optically thick model, and an 
optically thin model, respectively. The photometric data of the SMG are reported by \citet{Haas14}. \label{fig:SED}}
\end{figure}

\subsubsection{SMM J0939+8315} 
To constrain the dust and gas properties in the ISM of SMM J0939, we perform SED fitting on the
photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
between observed-frame 70 \micron-1000 \micron, and interferometric data with SMA at 1 mm (H14). We use the publicly
available software {\sc mbb\_emcee} to perform SED fitting, the code uses an affine-invariant Markov chain Monte
Carlo (MCMC) approach, the details are described by \citet{Riechers13a} and \citet{Dowell14a}. The
functional form of the fit comprises of a modified blackbody function with a power law S$_{\lambda} \propto \lambda^\alpha
$ attached to the blue
side.
We fit both an optically thick and optically thin model. In the optically thick case, the wavelength $
\lambda_0$ = $\frac{c}{\nu_0}$ is an additional parameter which represents where the optical
depth $\tau_{\nu}$ = ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
in the optically thick regime is as follows:
\begin{equation}
\rm S_{\lambda} \propto \frac{(1-exp^{-(\frac{\lambda_0 (1+z)}{\lambda})^{\beta}})(\frac{c}{\lambda})^3}
{exp^{\frac{hc}{\lambda\rm{kT/(1+z)} } }-1}
\end{equation}
and in the optically thin regime, the functional form reduces to:
\begin{equation}
\rm S_{\lambda} \propto \frac{(\frac{c}{\lambda})^{\beta+3}}{exp^{\frac{hc}{\lambda\rm{kT/(1+z)}}}-1}
\end{equation}
where T is the rest-frame characteristic cold dust temperature (fitting to the FIR part), $\lambda_0$ is rest-frame wavelength
where the optical depth reaches unity, $\beta$ is the dust emissivity (or spectral index of the dust extinction
curve), and $\alpha$ is the power law spectral index. The overall fit is normalized using the observed-frame 500
$\micron$ flux density, hence this becomes an additional parameter in the fit. In both models, we impose an upper limit on $
\lambda_0$ to 2000 \micron, and the observed-frame dust temperature $T_{\rm d}/(1+z)$ to 60 K. We fix the upper limit on 
$\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.

\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}. The best-fit solution of an optically thin
model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than the optically thin
model. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.33$^{+1.14}_{-1.13}\times$10$^{12}L_
\odot$, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.52$^{+2.62}_{-2.63}\times$10$
^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg\pmOne at 125.0 $
\micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
\begin{equation}
M_{\rm dust} = S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
\exp(-\tau_{\nu})]^{-1}
\end{equation}
where $S_{\nu}$ is the flux density, $D_{\rm L}$ is the luminosity distance, $\kappa_{\nu}$ is the dust
absorption coefficient, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$ =
50.47$^{20.42}_{-20.15}\times$10$^8$\Msun, the uncertainties do not include those of $\kappa_{\nu}$. These values are based on SED fitting to the photometric data, i.e. prior
to lensing correction.

\\ ======= I will edit this ======= 
With the limited amount of data in the FIR, $\beta$ and $M_{\rm dust}$ are weakly constrained (see appendix), we explore other possible blah.
We perform another fit imposing upper limit on beta to be 3.0, Hence, dust mass is blah
\\ ====================

%In most cases, $\alpha$ is poorly constrained, with the fits only providing a lower limit. Because of the way the
%blue-side power law is joined to the MBB,
%this simply amounts to a statement that the merge point between the power law and the thermal SED lies at
%wavelengths lower than the shortest
%wavelength photometry point (250 micron). (in Dowell et al. 2014)

\subsection{Molecular gas mass}
==== I will edit this ===== \\
Radford et al. (1991) calibration using local galaxies, calibrated H2 gas mass to CO L conversion using the cold gas (trace using G.S. CO), for high z galaxies with CO(higher J) line observations, make assumptions on the CO excitation conditions.

It has been long assumed that the molecular gas in the ISM traced by CO is thermalized given their high star formation rates (e.g. Greve et al. 2005; Coppin et al. 2008; Tacconi et al. 2008). With the few SMGs with CO(1-0) and higher J co observations to date,
Recent CO(1-0) observations of SMGs have demonstrated that SMGs can indeed be subthermally excited. (Bothwell et al. 2013, Harris et al. (2010). In these galaxies with subthermal excitation at the (3-2) transition, the brightness temperature ratio between CO(3-2) and CO(1-0) is $<$ 0.8. with an average radio of R31 = 0.6 pm 0.1 \citep[\eg][]{Harris10a,Carilli10a,Swinbank2010a,Ivison11a,Ivison10d}. While these brightness temperature ratios are blah in SMGs, observations of high-z quasars suggest that the host galaxies have ratios close to unity (e.g., Riechers 
et al. 2006; 2011a; Ivison et al. 2012). Since only \CO line has been detected on this object, we adopt 1 here since the source is hosting a quasar.
\\ ========

% Michalowski et al. 2010, Santini et al. 2010
% typical of local ULIRGs is ~ 100)
%\citep{Riechers11b}

We derive the molecular gas mass in
this SMG assuming thermalized excitation or assuming thermalized optically thick CO, i.e. the brightness temperature ratio 
between \CO
and ($J$ = 1 \rarr 0) is $R_{31}$ = 1 \citep[\eg][and references therein]{Riechers11a,Scott11a}
%(\eg Ivison et al. 2008, 2012). 
We calculate the CO($J$ = 1 \rarr 0) line luminosity using standard relations 
\citep[\eg][]{Solomon05a,Carilli13a}:
\begin{equation}
L^{\prime}_{\rm CO} = \frac{3.25\times10^7}{\nu_{\rm CO (3-2), rest}^2}\times \frac{D_L^2}{\mu} \times
\frac{I_{\rm CO(3-2)}} {R_{\rm 31} (1 + z)}
\end{equation}
this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ ($\mu$/9.74)\pmOne (\rm K km s
\pmOne pc$^2$)
after lensing correction. The inferred total molecular gas mass is therefore M$_{\rm gas}$ = (3.303$\pm$blah) $\times
$10$^{10}$ ($\alpha$/0.8) ($\mu$/9.74)$^{-1}$ \Msun. We assumed a conversion factor of $\alpha_{\rm CO}$ =
0.8 \Msun (\LpU)\pmOne based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep{Bothwell13a,Tacconi10a,Daddi2010a}. As derived in the previous section, SMM has a dust mass of $M_{\rm dust}
$=50.47$^{20.42}_{-20.15}\times$10$^8$ \Msun (before lensing correction), this corresponds to a gas-to-dust
ratio of $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , which is in good agreement with the range 
of values found in other SMGs (cite).

@@

\subsection{Star formation rate}
We derive the star formation rate (SFR) using the \citet{Kennicutt98a} relation, assuming a \citet{Chabrier03a}
stellar initial mass (IMF) function: SFR = 1.0 $\times$ 10$^{-10}\times$ ($L_{\rm IR\ or\ FIR}$). This yields SFR$_{\rm IR}$ 
= (909.12$\pm$155.67) $\times\ (\mu/9.74)^{-1}$ [$M\sun$ yr\pmOne] and SFR$_{\rm FIR}$ 547.71$\times(\mu/9.74)^{-1}$ [M$
\sun$ yr\pmOne] using lensing-corrected (far-)infrared luminosities (L$_{\rm IR}$ and L$_{\rm FIR}$) derived from our SED 
fitting, and assuming negligible contributions from AGN heating.

Assuming constant SFR, the minimum time for which the starburst in SMM J0939 can be maintained at its
current SFR is approximated by the gas depletion timescale $\tau$ = $M_{\rm gas}$/SFR, which is $\tau_{\rm IR}$ = 36.33 
Myr, and $\tau_{\rm FIR}$ = 60.30 Myr.

Move to discussion: Compare THIS NUMBER: with other SMGs (\eg \citep{Greve05a}).

\subsection{SFE}
% The ratio between LIR ($\propto$ SFR) and L$^\prime$CO ($\propto$ Mgas)
%Frayer: Since the IR luminosity is proportional to the SFR and the CO L is proportional to the molecular gas mass, the IR-to-
%CO L ratio provides an indication of the SFE. Strong starburst and ULIRGs tend to show high IR-to-CO L ratios of $\gtrsim$ 
%100 L$\sun$ ( K km/s pc2)-1 \citep[\eg][]{Solomon05a}. 
%\citet{Greve05a} found an average L(IR)/L$\prime
%$CO ratio for SMGs which was a factor of two larger than that for local ULIRGs

The SFR per unit mass of molecular gas is commonly taken as a
measure of the star formation efficiency, SFE = SFR/$M_{\rm gas}$. We compute the ratio using lensing-corrected (far-)infrared 
luminosities ($L_{\rm IR}$ and $L_{\rm FIR}$) and CO($J$ = 1 \rarr 0) luminosity SFE = $L_{\rm F/IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ and is independent of the 
choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible.

@@

We find a ratio of SFE$_{\rm IR}$ = 220.22 Myr\pmOne and SFE$_{\rm FIR}$ = 132.68 Myr\pmOne, which are comparable
to what is found in "typical" SMGs (tacconi et al. 2006, Riechers et al. 2010, cite).
%Note: SFE values for ULIRGs and distant SMGs typically exceed 100 \Lsun [K km/s pc$^2$]\pmOne
%(\eg Yao et al. 2003; Neri et al. 2003; Greve et al. 2005; Bouche et al. 2007).

\subsection{Dynamical mass} %% check half light radius error, and comparison
We derive the dynamical mass of SMM J0939 using an isotropic virial estimator \citep[\eg][]{Engel10a}:
\begin{equation}
M_{\rm dyn} = 2.8\times 10^5 \times \Delta \rm v_{\rm line}^ 2 \times r
\end{equation}
where the line width $\Delta \rm v_{\rm line}^ 2$ is based on our \CO line
measurement and $r$ is approximated with the half-light radius of the best-fit lens model. This yields $M_{\rm dyn}$ = blah, and gas-to-
dynamical mass fraction of $f_{\rm gas-to-dyn}$ = 2.03.\\ \\

\\ ===== That's it for now ==========
Compare to other. blah blah blah dynamical mass, is it consistent with molecular gas mass?

\subsection{SFR surface density}
% using dynamical mass and Eddington luminosity limit
To compute surface densities we divided half of the star formation rate or gas mass (so that no assumption of IMF) by the area subtended by the half-light (or effective) radius.

\section{Discussion And Conclusions} \label{sec:conclusions}
We present blah

@@

We compare the properties of SMM J0939 with two other SMGs with detailed studies -- HLSW-01 and the cosmic Eyelash. All sources are lensed, making spectral lines measurements relatively feasible than their fainter, un-lensed ``siblings".

Properties and comparison with similar galaxies in Table \ref{tab:comapreSMG}
\input{table_compareSMG}
Discussion of SMG, broad, population.
look at "Lensed QSOs at high z observational, CO measurements (DB)" note

\acknowledgments

We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
Facilities: \facility{CARMA}

@@

\appendix

\begin{figure}[!tbp]
\centering
\includegraphics[width=0.90\textwidth]{Figure/posteriorPDFs}
\caption{Figure shows the marginalized posterior probabilities of each parameter in our lens modeling.
\label{fig:LensPDF}}
\end{figure}
